A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-20 writeup/paper.tex
new quality scores

\section{Measuring Data Quality}
The primary challenge of using crowdsourced language data is the widely variable quality of the collected annotations. While it is possible to strengthen the signal by collecting redundant labels, this strategy becomes difficult in practice for more complex data annotation. In the case of translation, even professional translations can be expected to vary significantly, and fully automatic comparison of free form text is itself an open research question.

@@

Measured in this way, the average quality score across all HITs was just under 0.3. In general, countries which produced more translations did not produce lower quality translations, with India, Macedonia, and the US falling very close to average quality (figure \ref{quality-scatter}). In fact, likely as a result of the large number of India-based Turkers, most of the Indian languages fall above average quality, including Hindi, Telugu, Malayalam, Marathis, Tamil, Gujarati, Kannada, Bengali, and Punjabi, shown in figure \ref{hitlangqual-bar}. The notable exception is Urdu, which produced below average translations, likely due to the relatively low number of unique translators, making quality more susceptible to individual careless workers (see figure \ref{ass-scatter}).

>>>>

\section{Measuring Data Quality}
The primary challenge of using crowdsourced language data is the widely variable quality of the collected annotations. While it is possible to strengthen the signal by collecting redundant labels, this strategy becomes difficult in practice for more complex data annotation. In the case of translation, low quality translations may have a high level of agreement (for example, when many workers use google translate) while high quality, even professional translations, can be expected to vary significantly.

@@

Measured in this way, the average quality score across all HITs was just under \textbf{XXXX}. In general, countries which produced more translations did not produce lower quality translations, with India, Macedonia, and the US falling very close to average quality (figure \ref{quality-scatter}). In fact, likely as a result of the large number of India-based Turkers, most of the Indian languages fall above average quality, including Hindi, Telugu, Malayalam, Marathis, Tamil, Gujarati, Kannada, Bengali, and Punjabi, shown in figure \ref{hitlangqual-bar}. The notable exception is Urdu, which produced below average translations, likely due to the relatively low number of unique translators, making quality more susceptible to individual careless workers (see figure \ref{ass-scatter}).

### 2013-02-20 writeup/summary.tex
new quality scores

\begin{figure}[h]
\centering
\begin{tabular}{lccc}
\multicolumn{4}{c}{Number of turkers per language}\\
\hline\hline
&\multicolumn{2}{c}{Avg. turker quality (\# Turkers)}&In-region turker locations\\
&In region&Out of region\\
\hline\hline
Hindi&\textbf{0.54 (299)}&0.47 (63)&India (285) UAE (5) UK (5) Other (5) \\
Tamil&\textbf{0.55 (278)}&0.54 (26)&India (271) US (3) Canada (2) Other (2) \\
Malayalam&0.48 (235) &\textbf{0.55} (49)&India (224) UAE (6) US (3) Other (2) \\
Spanish&\textbf{0.27 (205)}&0.27 (39)&US (131) Mexico (18) Spain (14) Other (43) \\
French&0.29 (183) &\textbf{0.31} (34)&India (68) US (48) France (25) Other (42) \\
German&\textbf{0.35 (99)}&0.31 (71)&Germany (51) US (29) Austria (9) Other (11) \\
Italian&\textbf{0.32 (98)}&0.27 (68)&Italy (44) US (32) Romania (9) Other (13) \\
Chinese&\textbf{0.42 (123)}&0.41 (28)&US (80) Singapore (15) China (14) Other (21) \\
Telugu&\textbf{0.48 (102)}&0.41 (35)&India (98) US (3) UAE (1) \\
Malay&\textbf{0.30 (15)}&0.28 (116)&Malaysia (8) Singapore (4) US (2) Other (1) \\
\hline\hline
\end{tabular}
\end{figure}

>>>>

\begin{figure}[h]
\footnotesize
\begin{tabular}{llll}
\multicolumn{4}{c}{Number of turkers per language}\\
\hline\hline
&\multicolumn{2}{c}{Avg. turker quality (\# Turkers)}&Primary locations\\
&In region&Out of region&of turkers in region\\
\hline\hline
Hindi&\textbf{0.410} (299)&0.406 (63)&India (285) UAE (5) UK (5) \\
Tamil&0.339 (278) &\textbf{0.482} (26)&India (271) US (3) Canada (2) \\
Malayalam&\textbf{0.534} (235)&0.505 (49)&India (224) UAE (6) US (3) \\
Spanish&0.561 (205) &\textbf{0.682} (39)&US (131) Mexico (18) Spain (14) \\
French&\textbf{0.636} (183)&0.541 (34)&India (68) US (48) France (25) \\
German&\textbf{0.691} (99)&0.678 (71)&Germany (51) US (29) Austria (9) \\
Italian&0.650 (98) &\textbf{0.716} (68)&Italy (44) US (32) Romania (9) \\
Chinese&0.165 (123) &\textbf{0.207} (28)&US (80) Singapore (15) China (14) \\
Telugu&\textbf{0.582} (102)&0.582 (35)&India (98) US (3) UAE (1) \\
Malay&0.630 (15) &\textbf{0.649} (116)&Malaysia (8) Singapore (4) US (2) \\
Turkish&0.593 (83) &\textbf{0.634} (47)&Turkey (39) US (20) Macedonia (12) \\
Kannada&0.155 (106) &\textbf{0.284} (21)&India (106) US (1) \\
Portuguese&0.599 (107) &\textbf{0.651} (19)&Brazil (46) Portugal (32) US (15) \\
Arabic&\textbf{0.278} (62)&0.217 (64)&Egypt (19) Jordan (17) Morocco (9) \\
Romanian&0.653 (87) &\textbf{0.668} (37)&Romania (77) US (6) Moldova (3) \\
Swedish&0.497 (58) &\textbf{0.504} (66)&US (28) Sweden (23) Finland (3) \\
Czech&0.536 (52) &\textbf{0.571} (71)&US (19) Czechrepublic (15) Serbia (5) \\
Irish&\textbf{0.645} (58)&0.605 (64)&US (41) Ireland (13) UK (4) \\
Amharic&0.080 (17) &\textbf{0.138} (105)&US (14) Ethiopia (3) \\
Russian&0.202 (72) &\textbf{0.275} (49)&US (38) Russia (8) Moldova (7) \\
\hline\hline
\end{tabular}
\end{figure}
